Quantitative Sampling for \\ \texttt{Probabilistic Assert Failures}

### 2021-03-18 quant_estimate/pse_quant_algo.tex
WIP : Quant Example Draft

\title{PSE Quant Sampling Algorithm}
\author{Sumit Lahiri}

@@

We try to formulate a way to compute path probabilities using \texttt{symbolic execution} and \texttt{testing} based technique.
\begin{minted}{c} 
int main(void)
{
	int a; // unintialized
	int d = std::uniform_distribution<rd_seed>(0, 650);

@@

	// Probabilistic query : assert(P(c != d) < 0.5)
	// Optimize here : 
	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
	return 0;
}
\end{minted}

@@

	if (a > b) { // 
		if (c + e < 15) {
			win = 1;
			win_ones++;
		} else {
			...
		}
	} else {
		if (d + e > 1) {
			win = 1;
			win_ones++;
		} else {
			...
		}
	}
	run++;
} // P(win==1) is win_ones/run;
\end{minted}

@@

For other \texttt{candidate} vectors, we find that the \texttt{probabilistic} asserts actually hold and will not cause a violation during execution under normal condiditons.

>>>>

\title{Quantitative Sampling for \\ \texttt{Probabilistic Assert Failures}}
\author{Sumit Lahiri \\ \texttt{IIT Kanpur}}

@@

We try to formulate a way to compute path probabilities using \texttt{symbolic execution} and \texttt{testing} based technique.

\begin{minted}{c} 
int main(void)
{
	int a; // unintialized
	int d = std::uniform_distribution<rd_seed>(0, 650);

@@

	// Probabilistic query : assert(P(c != d) < 0.5)
	// Optimize here : 
	//	Optimal value of forall variable 'a' 
	//        such that P(c != d) is close to 0.5 	
	return 0;
}
\end{minted}

@@

	if (a > b) { // 
		if (c + e < 15) {
			win = 1;
			win_ones++;
		} else {
			...
		}
	} else {
		if (d + e > 1) {
			win = 1;
			win_ones++;
		} else {
			...
		}
	}
	run++;
}

// The probabilistic assert is the following
// assert(P(win == 1) >= 0.8), where P(win == 1) win_ones/run;

\end{minted}

@@

For other \texttt{candidate} vectors, we find that the \texttt{probabilistic} asserts actually hold and will not cause a violation during execution under normal condiditons. We show the results of some of the winning cases here.
